---
title: "R population_sizeotebook"
output: html_notebook
---


# liberaries

```{r}
library(tidyverse)
library(magrittr)
library(tictoc)
```


# Unbiased transmission
 
 
 unbiased (copied entirely at random) oblique (members of one generation learn from those of the previous, non-overlapping, generation) transmission... horizontal transmission (individuals copy members of the same generation) vertical transmission (offspring copy their biological parents)
 
 
```{r}
model_unbiased_transmission <- function(population_size, timesteps) {
  output <- tibble(timestep = 1:timesteps, proportion_of_trait_a = rep(NA, timesteps))
  population <- sample(c("A", "B"), population_size, replace = TRUE)

  output$proportion_of_trait_a[1] <- sum(population == "A") / population_size

  for (timestep in 2:timesteps) {
    previous_population <- population
    population <- sample(previous_population, population_size, replace = TRUE)
    output$proportion_of_trait_a[timestep] <- sum(population == "A") / population_size
  }
  output
}
data_unbiased_transmission <- model_unbiased_transmission(population_size = 100, timesteps = 20)
plot_single_run <- function(data) {
  ggplot(data = data, aes(x = timestep, y = proportion_of_trait_a)) +
    geom_line() +
    ylim(c(0, 1))
}
data_unbiased_transmission %>%
  plot_single_run()
```

multiple runs

```{r}
population <- sample(c("A", "B"), 1000, replace = TRUE)

# model_unbiased_transmissions does the same thing as unbiased_transmission_2(), but runs ~x8 times faster, and, imo, more human-readable.
model_unbiased_transmissions <- function(population_size, timesteps, runs) {
  output <- tibble(run = numeric(), timestep = numeric(), proportion_of_trait_a = numeric())
  for (run in 1:runs) {
    # initialize output dataframe
    output_single_run <- tibble(run = rep(run, timesteps), timestep = 1:timesteps, proportion_of_trait_a = rep(NA, timesteps))
    # initialize population
    population <- sample(c("A", "B"), population_size, replace = TRUE)
    # initialize first generation's p
    proportion_of_trait_a <- sum(population == "A") / population_size
    output_single_run$proportion_of_trait_a[1] <- proportion_of_trait_a
    for (timestep in 2:timesteps) {
      previous_population <- population
      population <- sample(previous_population, population_size, replace = TRUE)
      output_single_run$proportion_of_trait_a[timestep] <- sum(population == "A") / population_size
    }
    output <- bind_rows(output, output_single_run)
  }
  output
}
tic()
data_unbiased_transmissions <- model_unbiased_transmissions(100, 100, 10)
toc()
```
plot 

```{r}
model_unbiased_transmissions(100, 100, 10) %>%
  ggplot(aes(x = timestep, y = proportion_of_trait_a)) +
  geom_line(aes(colour = as.factor(run))) +
  stat_summary(fun = mean, geom = "line", size = 1) +
  ylim(c(0, 1))
```
田村(2020: 59)の図2.14に対応する。

```{r}
model_unbiased_transmissions(100, 100, 100) %>%
  ggplot(aes(x = timestep, y = proportion_of_trait_a)) +
  geom_line(aes(group = as.factor(run)), size = 0.1) +
  stat_summary(fun = mean, geom = "line", size = 1) +
  ylim(c(0, 1)) +
  theme(legend.position = "none")
```
random fluctuations of the proportion of trait A under unbiased cultural transmission, due to the stochastic nature of the simulation.

## Varying initial conditions

```{r}
model_unbiased_transmissions_varying_initial_condition <- function(population_size, initial_probability_of_trait_a, timesteps, runs) {
  output <- tibble(run = numeric(), timestep = numeric(), proportion_of_trait_a = numeric())
  for (run in 1:runs) {
    # initialize output dataframe
    output_single_run <- tibble(run = rep(run, timesteps),timestep = 1:timesteps, proportion_of_trait_a = rep(NA, timesteps))
    # initialize population
    population <- sample(c("A", "B"), population_size, replace = TRUE, prob = c(initial_probability_of_trait_a, 1 - initial_probability_of_trait_a))
    # initialize first generation's p
    proportion_of_trait_a <- sum(population == "A") / population_size
    output_single_run$proportion_of_trait_a[1] <- proportion_of_trait_a
    for (timestep in 2:timesteps) {
      previous_population <- population
      muat
      population <- sample(previous_population, population_size, replace = TRUE)
      output_single_run$proportion_of_trait_a[timestep] <- sum(population == "A") / population_size
    }
  output <- bind_rows(output, output_single_run)
  }
  output
}

  model_unbiased_transmissions_varying_initial_condition(10000, 0.2, 200, 5) %>% 
    ggplot(aes(x = timestep, y = proportion_of_trait_a)) +
    geom_line(aes(colour = as.factor(run))) +
    stat_summary(fun = mean, geom = "line", size = 1) +
    ylim(c(0, 1))
```


 
